\thetitle

### 2020-11-02 sun_phases/spin_qudit_tomo.tex
minor claims to commentary about computing the overlap matrix, and added a reference to a yet unwritten appendix about computing the error bound

The complexity of computing $\M_V^2$ is determined by the need to:
\begin{enumerate*}
\item compute all rotated transition operators $T_{\v v\ell,0}$, which by the expansion $T_{\v v\ell,0}=R\p{\v v}T_{\ell,0}R\p{\v v}^\dag$ takes $O(\abs{V}d^4)$ serial or $O(d^3)$ parallel runtime;
\item construct the overlap matrix $G_V$, whose block diagonal structure makes possible in $O(\abs{V}^2d^3)$ serial or $O(\abs{V}^2d^2)$ parallel runtime; and
\item diagonalize the blocks of $G_V$, which takes $O(\abs{V}^3d)$ serial or $O(\abs{V}^3)$ parallel runtime.
\end{enumerate*}
Altogether, assuming $\abs{V}\propto d$ the bound in Eq.~\eqref{eq:bound} can be certified in $O(d^5)$ serial or $O(d^4)$ parallel runtime.
In practice, for modest values of $d$ we find that vectorized operations can reduce serial runtime to $\sim O(r^4)$, and that serial execution time is divided about evenly between computing rotated transition operators $T_{\v v\ell,0}$ and constructing the overlap matrix $G_V$, with a negligible amount of time spent on diagonalization (see Figure [\red{REF}]).  [\red{todo: add figure showing runtime for each routine as a function of $d$ with $\abs{V}=2d-1$; modify text appropriately after making the figure}].
We suspect that more efficient representations of the transition operators $T_{\ell m}$, namely as $\p{2\ell+1}$-component vectors rather than $d\times d$ matrices, together with appropriate changes to the representation of the adjoint rotation operator $\R\p{\v v}$, should reduce the computational complexity of computing $\M_V^2$ by a factor of $O(d)$.

@@

>>>>

The complexity of computing $\M_V^2$ is determined by the need to:
\begin{enumerate*}
\item compute all rotated transition operators $T_{\v v\ell,0}$, which by the expansion $T_{\v v\ell,0}=R\p{\v v}T_{\ell,0}R\p{\v v}^\dag$ takes $O(\abs{V}d^4)$ serial or $O(d^3)$ parallel runtime;
\item construct the overlap matrix $G_V$, whose block diagonal structure makes possible in $O(\abs{V}^2d^3)$ serial or $O(\abs{V}^2d^2)$ parallel runtime; and
\item diagonalize the blocks of $G_V$, which takes $O(\abs{V}^3d)$ serial or $O(\abs{V}^3)$ parallel runtime.
\end{enumerate*}
We discuss these calculations in more detail in Appendix \ref{sec:overlaps}.
Altogether, assuming $\abs{V}\propto d$ the bound in Eq.~\eqref{eq:bound} can be certified in $O(d^5)$ serial or $O(d^4)$ parallel runtime.
In practice, for modest values of $d$ we find that serial execution time is divided about evenly between computing rotated transition operators $T_{\v v\ell,0}$ and constructing the overlap matrix $G_V$, with a negligible amount of time spent on diagonalization (see Figure [\red{REF}]).  [\red{todo: add figure showing runtime for each routine as a function of $d$ with $\abs{V}=2d-1$; modify text appropriately after making the figure}].
We suspect that more efficient representations of the transition operators $T_{\ell m}$, namely as $\p{2\ell+1}$-component vectors rather than $d\times d$ matrices, together with appropriate changes to the representation of the adjoint rotation operator $\R\p{\v v}$, can reduce the complexity of computing $\M_V^2$ by a factor of $O(d)$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Computing the overlap matrix}
\label{sec:overlaps}

[\red{todo: walk through the calculation of the error scale $\M_V$.}]
